Auditory Scene Similarity Retrieval and Classification with Relevance based Quantization of Scattering Features

### 2016-12-13 paper/structureScene.tex
Add MFCC + SVM results

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset for the baseline algorithm (left) and proposed algorithm (right).}
\begin{tabular}{lccc}
Features & MFCCs & MFCCs & log-scattering \\
Classifier  & GMMs & linear SVMs & linear SVMs \\
Variant of \emph{late} integration & product & majority vote & majority vote \\
\midrule
beach & $74.6 \pm 18.9$ & & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & & $88.8 \pm 11.4$ \\
caf\'{e} / restaurant & $85.1 \pm 10.8$ & & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & & $94.9 \pm \phantom{0}6.1$ \\
city center & $89.6 \pm \phantom{0}9.2$ & & $91.7 \pm \phantom{0}9.4$ \\
forest path & $72.4 \pm 23.8$ & & $93.8 \pm \phantom{0}7.8$ \\
grocery store & $74.1 \pm 13.7$ & & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & & $82.0 \pm 13.0$ \\
metro station & $85.2 \pm 15.6$ & & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & & $75.4 \pm \phantom{0}7.4$ \\
residential area & $75.1 \pm 19.4$ & & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & & $79.4 \pm \phantom{0}3.0$
\end{tabular}
\end{center}
\label{table:dcase2016}
\end{table}

>>>>

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset for the baseline algorithm (left) and proposed algorithm (right).}
\begin{tabular}{lccc}
Features & MFCCs & MFCCs & log-scattering \\
Classifier  & GMMs & linear SVMs & linear SVMs \\
Variant of \emph{late} integration & product & majority vote & majority vote \\
\midrule
beach & $74.6 \pm 18.9$ & $58.3 \pm 28.2$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & $58.2 \pm 25.4$ & $88.8 \pm 11.4$ \\
cafe/restaurant & $85.1 \pm 10.8$ & $77.4 \pm 14.7$ & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & $92.3 \pm \phantom{0}7.7$ & $94.9 \pm \phantom{0}6.1$ \\
city\_center & $89.6 \pm \phantom{0}9.2$ & $96.4 \pm \phantom{0}3.8$ & $91.7 \pm \phantom{0}9.4$ \\
forest\_path & $72.4 \pm 23.8$ & $67.7 \pm 30.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery\_store & $74.1 \pm 13.7$ & $44.7 \pm 24.8$ & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & $44.8 \pm 15.3$ & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & $54.6 \pm 20.3$ & $82.0 \pm 13.0$ \\
metro\_station & $85.2 \pm 15.6$ & $94.7 \pm \phantom{0}6.8$ & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & $95.7 \pm \phantom{0}7.5$ & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & $52.4 \pm 10.4$ & $75.4 \pm \phantom{0}7.4$ \\
residential\_area & $75.1 \pm 19.4$ & $53.2 \pm 17.0$ & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & $44.5 \pm 23.1$ & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & $52.1 \pm 11.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & $65.8 \pm \phantom{0}8.0$ & $79.4 \pm \phantom{0}3.0$ \\
\end{tabular}
\end{center}
\label{table:dcase2016}
\end{table}
